%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Shiv Nadar University} % Organisation
    {Mediline} % Project
    {Greater Noida, India} % Location
    {currently working} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Webapp development to find the diseases using machine learning models and industry level front-end development}
        \item {. There are separate webpages created for doctor and patient separately. Users can access the personal records of himself, his previous reports and so on. And so does the doctor only if an appointment is booked to avoid data privacy issues. A machine learning model is being deployed to understand and predict the disease..}
        \item {\textbf{Languages:}  HTML, Tailwind CSS, Node.js, MongoDB.}
        \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Report writing.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {University of Leeds} % Organisation
    {IPL Analysis} % Project
    {Leeds, UK} % Location
    {Nov 2021 - Dec 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Analysing data from 2008 to 2015 to discover patterns such as trends, correlations, and probabilities.}
        \item {Finding the differences between the best teams and players in various fields, as well as their performance on the field and the opponents.}
        \item {\textbf{Technical Skills:} Python with Pandas, matplotlib, Seaborn.}
        \item {\textbf{Soft Skills:} Presentation skills, Leadership, Teamwork, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Shiv Nadar University} % Organisation
    {Library Management System} % Project
    {Greater Noida, India} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Study of serial killers behavior with various motives such as convenience (did not want children or spouse), enjoyment, power, escape, or avoiding arrest.}
        \item {Finding patterns in their starting and ending ages (when they are caught) and other factors of killing, as well as how it varies with different motives.}
        \item {\textbf{Technical Skills:} R with ggplot2, tidyr, R Markdown.}
        \item {\textbf{Soft Skills:} Report writing, Logical Thinking, Critical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
